Type-Safe Modular Parsing

### 2017-01-14 paper/sections/RelatedWork.tex
Added the last paragraph in S7.

\paragraph{Extensible Parsing Algorithms}
Extensible parsing algorithms are another area that relates to
separate compilation.
\textit{Parse table composition}~\cite{Bravenboer2009}
is an approach where grammars are compiled to
modular parse tables. Those parse tables are expressed as DFAs
or NFAs, and later they can be composed by an algorithm, to provide
separate compilation for parsing. The generation of parse tables can
be quite expensive in terms of performance. The approach
is quite different from ours, since it uses parse
 tables, whereas we use parser combinators.
Our approach supports both
\emph{separate compilation} as well as \emph{modular
  type-checking}. Moreover, the extensibility of parsing is further
available at language composition and lexical level.

@@

Another interesting observation, as we have mentioned
in Section~\ref{subsec:more-oa}, is that transformation algebras are
frequently used in parsing, as concrete syntax may not always coincide
with its abstract syntax, for instance, the bruijn indices in lambda
calculus, as well as other syntactic sugars. In the Shy
framework~\cite{Zhang2015}, the pattern of transformations is captured
into a template for Java annotation processing, and most of
boilerplate code is automatically generated, hence users only need to
override a few interesting cases, conveniently. It is potentially
useful in our case. The idea of overriding existing cases was also
proposed in MRM. Our approach allows existing parsing code to be
overridden during inheritance.

>>>>

\paragraph{Extensible Parsing Algorithms}
Extensible parsing algorithms are another area that relates to
separate compilation.
\textit{Parse table composition}~\cite{bravenboer2008parse}
is an approach where grammars are compiled to
modular parse tables. Those parse tables are expressed as DFAs
or NFAs, and later they can be composed by an algorithm, to provide
separate compilation for parsing. The generation of parse tables can
be quite expensive in terms of performance. The approach
is quite different from ours, since it uses parse
 tables, whereas we use parser combinators.
Our approach supports both
\emph{separate compilation} as well as \emph{modular
  type-checking}. Moreover, the extensibility of parsing is further
available at language composition and lexical level.

@@

Another interesting observation from Section~\ref{4}, is that parsers with
Object Algebras generate ``implicit objects'', which are actually functions of
type \lstinline{Alg[E]} \lstinline{=>} \lstinline{E} for generic \lstinline{E}.
Patterns of operations on such functions are captured by the original paper~\cite{Oliveira:2012}, called
\textit{queries} and \textit{transformations}, together with the composition of algebras.
They are quite useful, for instance, we have two operations (like the aforementioned \lstinline{Print} and \lstinline{Eval}) to be fed to the parser. If we feed them separately, it is tedious to parse the same input twice. Instead we can compose them in advance before the feeding. On the other hand, one would think this pattern is too limited to use against objects that traditional parsers generate. For example, there are a lot of transformations (or desugarings) on intermediate ASTs in the design of a compiler. Transformation algebras are helpful in that case. They can even be composed in a linear pipeline-style before a query algebra is delegated. The Shy framework~\cite{Zhang2015} has captured those patterns, and it generates templates for them, so that users only need to override a few interesting cases, conveniently. The idea of overriding existing cases was also
proposed in MRM~\cite{Oliveira2015}. They are potentially useful to our approach. Regarding overriding, our approach allows existing parsing code to be overridden during inheritance.
